Bridging Gaps: Investigating COVID-19's Influence on Health Disparities in Connecticut

### 2023-12-15 manuscript/manuscript.tex
added multiple comparison by year and town graphs

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage{tabularx}
\usepackage{adjustbox}

@@

\ref{tab:Demographics}
\ref{fig:Income by County Graph}

\begin{table}[h]
\label{tab:Demographics}
  \caption{Demographics and Education Levels for Counties 1-4}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lccccc}
    \toprule
    \textbf{Category} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} \\
    \midrule
    Total Population & 944,977 & 894,465.25 & 182,657.5 & 163,318.25 \\
    Race (Percent) & & & & \\
    \quad American Indian and Alaska Native & 0.24 & 0.3075 & 0.2025 & 0.195 \\
    \quad Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 \\
    \quad Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 \\
    \quad Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 \\
    \quad White & 72.6325 & 70.67 & 92.6025 & 88.0875 \\
    Ethnicity (Percent) & & & & \\
    \quad Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 \\
    Education (Percent) & & & & \\
    \quad Associates & 20.74 & 25 & 27.9225 & 26.46 \\
    \quad Bachelor & 26.53 & 21.4575 & 20.635 & 23.3325 \\
    \quad Graduate Degree & 21.14 & 16.475 & 14.6975 & 18.4525 \\
    \quad HS Graduate & 21.4725 & 26.7175 & 29.5875 & 26.0275 \\
    \quad Less than High School & 10.12 & 10.3525 & 7.1575 & 5.7275 \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

\begin{table}[h]
  \label{tab:Demographics}
  \caption{Demographics and Education Levels for Counties 5-8}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lcccc}
    \toprule
    \textbf{Category} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\
    \midrule
    Total Population & 858,678 & 268,477.75 & 151,218.75 & 116,608.75 \\
    Race (Percent) & & & & \\
    \quad American Indian and Alaska Native & 0.1725 & 0.605 & 0.05 & 0.565 \\
    \quad Asian & 4.005 & 4.12 & 4.675 & 1.3675 \\
    \quad Black or African American & 13.34 & 5.8175 & 3.1075 & 2.33 \\
    \quad Native Hawaiian and Pacific Islander & 0.0225 & 0.025 & 0 & 0.015 \\
    \quad White & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
    Ethnicity (Percent) & & & & \\
    \quad Hispanic & 17.885 & 10.5 & 5.4475 & 11.6375 \\
    Education (Percent) & & & & \\
    \quad Associates & 24.4175 & 29.2675 & 26.315 & 30.9775 \\
    \quad Bachelor & 18.785 & 18.3175 & 23.4075 & 14.595 \\
    \quad Graduate Degree & 16.3425 & 15.18 & 17.865 & 9.55 \\
    \quad HS Graduate & 30.565 & 29.46 & 27.03 & 33.5125 \\
    \quad Less than High School & 9.8875 & 7.7725 & 5.385 & 11.365 \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

\begin{figure}[tbp]
  \label{fig:Income by County Graph}
    \centering
    \includegraphics[width=\textwidth]{Income by County Graph.pdf}
    \caption{Median Income by County.}
  \end{figure}

@@

@@

  Fairfield County & Hartford County & 20565.50000* & 1883.47243 & \textbf{<.001} & 14327.6034 & 26803.3966 \\
  & Litchfield County & 14919.50000* & 1883.47243 & \textbf{<.001} & 8681.6034 & 21157.3966 \\
  & Middlesex County & 9671.75000* & 1883.47243 & \textbf{<.001} & 3433.8534 & 15909.6466 \\
  & New Haven County & 25662.75000* & 1883.47243 & \textbf{<.001} & 19424.8534 & 31900.6466 \\
  & New London County & 21456.50000* & 1883.47243 & \textbf{<.001} & 15218.6034 & 27694.3966 \\
  & Tolland County & 8705.00000* & 1883.47243 & \textbf{0.002} & 2467.1034 & 14942.8966 \\
  & Windham County & 28671.00000* & 1883.47243 & \textbf{<.001} & 22433.1034 & 34908.8966 \\

@@

  & Windham County & 8105.50* & 1883.47 & 0.005 & 1867.60 & 14343.40 \\

@@

  Middlesex County & Fairfield County & -9671.75* &  & 1883.47 & <.001 & -15909.65 & -3433.85 \\
  & Hartford County & 10893.75* & 1883.47 & <.001 & 4655.85 & 17131.65 \\

@@

  & New Haven County & 15991.00* & 1883.47 & <.001 & 9753.10 & 22228.90 \\
  & New London County & 11784.75* & 1883.47 & <.001 & 5546.85 & 18022.65 \\

@@

  & Windham County & 18999.25* & 1883.47 & <.001 & 12761.35 & 25237.15 \\

@@

  New Haven County & Fairfield County & -25662.75* &  & 1883.47 & <.001 & -31900.65 & -19424.85 \\

@@

  & Windham County & 3008.25 & 1883.47 & 0.747 & -3229.65 & 9246

@@

  Windham County & Fairfield County & -28671.00* &  & 1883.47 & <.001 & -34908.90 & -22433.10 \\

@@

@@

@@

>>>>

%% preamble: Keep it clean; only include those you need
\usepackage{amsmath}
\usepackage[margin = 1in]{geometry}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{natbib}
% for space filling
\usepackage{lipsum}
% highlighting hyper links
\usepackage[colorlinks=true, citecolor=blue]{hyperref}
\usepackage{tabularx}
\usepackage{adjustbox}
\usepackage[utf8]{inputenc}

@@

\ref{tab:Demographics1}
\ref{tab:Demographics2}

\ref{fig:Education by County Graph}
discuss, use lit to support why

\ref{fig:Social Needs by County Graph}
differences by year

\ref{tab:Multiple Comparison for Income}
the specific values for income

\ref{tab: Multiple Comparisons}
what discussion talks about

\begin{table}[h]
\label{tab:Demographics1}
  \caption{Demographics and Education Levels for Counties 1-4}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lccccc}
    \toprule
    \textbf{Category} & \textbf{Fairfield County} & \textbf{Hartford County} & \textbf{Litchfield County} & \textbf{Middlesex County} \\
    \midrule
    Total Population & 944,977 & 894,465.25 & 182,657.5 & 163,318.25 \\
    Race (Percent) & & & & \\
    \quad American Indian and Alaska Native & 0.24 & 0.3075 & 0.2025 & 0.195 \\
    \quad Asian & 5.2925 & 5.2925 & 1.9 & 3.0625 \\
    \quad Black or African American & 11.405 & 13.7025 & 1.83 & 5.385 \\
    \quad Native Hawaiian and Pacific Islander & 0.055 & 0.035 & 0 & 0.005 \\
    \quad White & 72.6325 & 70.67 & 92.6025 & 88.0875 \\
    Ethnicity (Percent) & & & & \\
    \quad Hispanic & 19.53 & 17.8275 & 6.15 & 6.12 \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

\begin{table}[h]
  \label{tab:Demographics2}
  \caption{Demographics and Education Levels for Counties 5-8}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{lcccc}
    \toprule
    \textbf{Category} & \textbf{New Haven County} & \textbf{New London County} & \textbf{Tolland County} & \textbf{Windham County} \\
    \midrule
    Total Population & 858,678 & 268,477.75 & 151,218.75 & 116,608.75 \\
    Race (Percent) & & & & \\
    \quad American Indian and Alaska Native & 0.1725 & 0.605 & 0.05 & 0.565 \\
    \quad Asian & 4.005 & 4.12 & 4.675 & 1.3675 \\
    \quad Black or African American & 13.34 & 5.8175 & 3.1075 & 2.33 \\
    \quad Native Hawaiian and Pacific Islander & 0.0225 & 0.025 & 0 & 0.015 \\
    \quad White & 73.2875 & 80.6175 & 88.025 & 88.8725 \\
    Ethnicity (Percent) & & & & \\
    \quad Hispanic & 17.885 & 10.5 & 5.4475 & 11.6375 \\
    \bottomrule
  \end{tabular}%
  }
\end{table}

\begin{figure}[tbp]
  \label{fig:Education by County Graph}
    \centering
    \includegraphics[width=\textwidth]{Education Levels by County.pdf}
    \caption{Education Levels by County.}
  \end{figure}

\begin{figure}[tbp]
  \label{fig:Social Needs by County Graph}
    \centering
    \includegraphics[width=\textwidth]{Multiple Comparisons by County.pdf}
    \caption{Social Needs Multiple Comparisons by County.}
  \end{figure}

@@

    \label{tab:Multiple Comparison for Income}
    \caption{Median Income Multiple Comparison by County}

@@

    Fairfield County & Hartford County & 20565.50* & 1883.47 & \textbf{\textless 0.001} & 14327.60 & 26803.40 \\
    & Litchfield County & 14919.50* & 1883.47 & \textbf{\textless 0.001} & 8681.60 & 21157.40 \\
    & Middlesex County & 9671.75* & 1883.47 & \textbf{<.001} & 3433.85 & 15909.65 \\
    & New Haven County & 25662.75* & 1883.47 & \textbf{<.001} & 19424.85 & 31900.65 \\
    & New London County & 21456.50* & 1883.47 & \textbf{<.001} & 15218.60 & 27694.40 \\
    & Tolland County & 8705.00* & 1883.47 & \textbf{0.002} & 2467.10 & 14942.90 \\
    & Windham County & 28671.00* & 1883.47 & \textbf{<.001} & 22433.10 & 34908.90 \\

@@

    & Windham County & 8105.50* & 1883.47 & \textbf{0.005} & 1867.60 & 14343.40 \\

@@

    Middlesex County & Fairfield County & -9671.75* & 1883.47 & \textbf{<.001} & -15909.65 & -3433.85 \\
    & Hartford County & 10893.75* & 1883.47 & \textbf{<.001} & 4655.85 & 17131.65 \\

@@

    & New Haven County & 15991.00* & 1883.47 & \textbf{<.001} & 9753.10 & 22228.90 \\
    & New London County & 11784.75* & 1883.47 & \textbf{<.001} & 5546.85 & 18022.65 \\

@@

    & Windham County & 18999.25* & 1883.47 & \textbf{<.001} & 12761.35 & 25237.15 \\

@@

    New Haven County & Fairfield County & -25662.75* & 1883.47 & <.001 & -31900.65 & -19424.85 \\

@@

    & Windham County & 3008.25 & 1883.47 & 0.747 & -3229.65 & 9246 \\

@@

    Windham County & Fairfield County & -28671.00* & 1883.47 & <.001 & -34908.90 & -22433.10 \\

@@

    \bottomrule

@@

\begin{table}[]
  \label{tab: Multiple Comparisons}
  \caption{Multiple Comparisons by Year and Town}
  \resizebox{\columnwidth}{!}{%
  \begin{tabular}{llrrrrl}
  \textbf{Social Need}   & \textbf{Comparison by} & \multicolumn{1}{l}{\textbf{DF}} & \multicolumn{1}{l}{\textbf{Sum of Squares}} & \multicolumn{1}{l}{\textbf{Mean Square}} & \multicolumn{1}{l}{\textbf{F Value}} & \textbf{P Value}           \\
  Median Income          & Year                   & 3                               & 158657606                                   & 52885869                                 & 95.57                                & <.0001                     \\
                         & Town                   & 7                               & 2618521106                                  & 374074444                                & 675.99                               & <.0001                     \\
  Food                   & Year                   & 3                               & 3.6450625                                   & 1.2150208                                & 10.08                                & 0.0003 \\
                         & Town                   & 7                               & 348.3382875                                 & 49.7626125                               & 412.72                               & <.0001                     \\
  Housing                & Year                   & 3                               & 1.4535125                                   & 0.4845042                                & 0.41                                 & 0.7506 \\
                         & Town                   & 7                               & 183.9498375                                 & 26.2785482                               & 21.99                                & <.0001                     \\
  Rehospitalization Rate & Year                   & 3                               & 0.00050938                                  & 0.00016979                               & 1.45                                 & 0.2578 \\
                         & Town                   & 7                               & 0.00427188                                  & 0.00061027                               & 5.2                                  & 0.0015 \\
  Uninsured Rate         & Year                   & 3                               & 2.6848375                                   & 0.89494583                               & 17.17                                & <.0001                     \\
                         & Town                   & 7                               & 92.8554875                                  & 13.26506964                              & 254.57                               & <.0001                    
  \end{tabular}%
  }
  \end{table}

@@

The results pertaining to housing defined by renters whose rent is 50 percent of their income, 
reveal noteworthy patterns with respect to social needs. Examining the data across the four-year span 
indicates a consistent trend, as no significant differences were observed. However, significant differences are 
revealed when comparing between counties. Counties 1 and 5 exhibited a statistically significant increase 
in the percentage of renters facing housing costs amounting to 50 percent of their income compared to 
counties 2, 7, and 3. Intriguingly, there was no statistically significant distinction between counties 
1 and 5, suggesting a commonality in the challenges faced by renters in these specific regions. These 
findings underscore the importance of localized interventions and policy considerations to address the 
distinct socio-economic dynamics influencing housing affordability across different counties.

Food access was assesses through investigating the proportion of the population involved in the use of Food Stamps programs.
AHRQ data reveals notable variations across different counties. Counties 8, 2, and 5 exhibit a statistically significant 
higher percentage of the population relying on Food Stamps, suggesting a potentially elevated level of economic 
vulnerability or socio-economic challenges in these areas. County 6 also demonstrates a substantial proportion 
of its population on Food Stamps, indicating a notable need for social assistance. Conversely, County 7 stands 
out with the lowest percentage of its population depending on Food Stamps, implying comparatively better 
economic conditions or potentially more effective social support systems. These findings underscore the 
importance of targeted interventions and resource allocation to address social needs, particularly in counties 
with higher reliance on Food Stamps. Further exploration into the underlying factors contributing to these variations 
is needed for informed policy development and community-specific interventions.
